SKETCH RECOGNITION AND UNDERSTANDING

### 2009-10-14 draft/SketchMaster.tex

% During the editing process you will not want to view and print the
% whole document. Uncomment the command below so that only the
% chapters that you want to work on are visible.
%\includeonly{ChapterIntroduction}
%\documentstyle[11pt,unhthesis]{report}
\documentclass[11pt,doublespace]{SketchThesis}

@@

\begin{document}
                                                        % TITLE PAGE
                                                        %======================
\title{SKETCH RECOGNITION AND UNDERSTANDING}            % My theses title  using Particle Swarm Optimization
% Algorithm   Sketch Recognition and Understanding
\author{Maha Mohamed Nabeel El Meseery Moustafa El Meseery}                               % Y name
\prevdegrees{B.S.,Computer Engineering}       		% Your old degree
\major{COMPUTER ENGINEERING}                            % My current major
\degree{MASTER OF SCIENCE}                              % My new degree
\degreemonth{July}                                      % When awarded. to be added when known
\degreeyear{2009}      
\FacultyUniversity{Faculty of Engineering, Cairo University \\ Giza, Egypt \\ July 2009}
\superad{}                                %
%\superad{Professor Nevin Darwish\\Professor Samia Mashali\\Assoc. Professor Magda Fayek\\}
%th today or first day of writing  December 26 2005 
%\thesisdate[]                                     % Date of document.
\DOCUMENTtype{ Thesis }                                   % or DISSERTATION
\Documenttype{ Thesis }                                   % or Dissertation
\documenttype{ Thesis }                                   % or dissertation

@@

                                                        % COPYRIGHT PAGE
                                                        %======================
%\copyrightyear{2009}                                    % Delete these
%\makecopyright                                          % if no copyright
  %=======================================Supervisors page ===============================
\newpage    
\thispagestyle{empty}               % Don't do headers or footers.                                                  
 \begin{center}     
 SKETCH RECOGNITION AND UNDERSTANDING\\
\normalsize by      \\ 
  Maha Mohamed Nabeel El Meseery Moustafa El Meseery\\
\vspace*{0.4in}        
\normalsize
A Thesis Submitted To the\\
Faculty of Engineering, Cairo University\\
in Partial Fulfillment of the\\
Requirements for the Degree of\\
MASTER OF SCIENCE
in\\
COMPUTER ENGINEERING\\
\vspace*{0.4in} 
Under the Supervision of 
\end{center}
  \vspace*{0.4in} 
\begin{center}
 		\begin{tabular}{ccc}
		Dr. Nevin Darwish  & Dr. Samia Mashali & Dr. Magda Fayek \\
		 Professor   & Professor & Associate Professor  \\
		 Faculty of Engineering& Electronic Research Institute & 		 Faculty of Engineering \\
		  Cairo University && Cairo University\\
		\end{tabular}
\end{center}
  \vspace*{0.4in}       
  \vfill
\begin{center}
   Faculty of Engineering, Cairo University \\ Giza, Egypt \\ July 2009
\end{center}

@@

%\begin{spacing}{2}
% \makebox[5in]{\hrulefill}\\ 
%Professor Nevin Darwish, Thesis Main Advisor\\
% \makebox[5in]{\hrulefill}\\ 
%Professor Samia Mashali,Thesis Advisor \\
% \makebox[6in]{\hrulefill}\\  
%Assoc. Professor Magda Fayek,Thesis Advisor\\ 
% \makebox[5in]{\hrulefill}\\ 
%Professor  Ashraf Abd El Wahab, Member\\
% \makebox[6in]{\hrulefill}\\ 
%Professor Mohamed Zaki Abd ElMegeed, Member\\
% \makebox[6in]{\hrulefill}\\ 
 %\end{spacing}
 \begin{center}
   Faculty of Engineering, Cairo University \\ Giza, Egypt \\ July 2009
\end{center}
  % \\   you need...\\
%\makeapproval                                           %

@@

 I thank my family and friends for their moral and support. I specifically thank, dina said, noha mansour and marwah shafee. Thanks, for being always there when I needed you the most. I hope to express my gratitude to all of you for supporting me and praying for me through all these years.
 %Finally, I am very grateful to my dear parents, my family, and my friends whom I consider
%as my sisters. I would like to thank particularly Radwa Aboudina, Fatma Nada, Maha
%Nabil, Haidi Badr, and Marwa Kamal. Thank you all for being always there when I needed
%you most. Thank you for believing in me and supporting me through all these years. I think
%without your support and your prayers, none of this work would be accomplished.
%ii
 \end{acknowledgments}                                   %

>>>>

% During the editing process you will not want to view and print the
% whole document. Uncomment the command below so that only the
% chapters that you want to work on are visible.
%\includeonly{ChapterIntroduction}
%\documentstyle[11pt,unhthesis]{report}
\documentclass[12pt,onehalfspacing]{SketchThesis}

@@

\begin{document}
                                                        % TITLE PAGE
                                                        %======================
\title{SKETCH RECOGNITION AND UNDERSTANDING}            % My theses title  using Particle Swarm Optimization
% Algorithm   Sketch Recognition and Understanding
\author{Maha Mohamed Nabeel El Meseery Moustafa El Meseery}                               % Y name
\prevdegrees{B.S.,Computer Engineering}       		% Your old degree
\major{COMPUTER ENGINEERING}                            % My current major
\degree{MASTER OF SCIENCE}                              % My new degree
\degreemonth{ }                                      % When awarded. to be added when known
\degreeyear{2009}      
\FacultyUniversity{Faculty of Engineering, Cairo University \\ Giza, Egypt \\  2009}
\superad{}                                %
%\superad{Professor Nevin Darwish\\Professor Samia Mashali\\Assoc. Professor Magda Fayek\\}
%th today or first day of writing  December 26 2005 
%\thesisdate[]                                     % Date of document.
\DOCUMENTtype{ Thesis }                                   % or DISSERTATION
\Documenttype{ Thesis }                                   % or Dissertation
\documenttype{ Thesis }                                   % or dissertation

@@

                                                        % COPYRIGHT PAGE
                                                        %======================
%\copyrightyear{2009}                                    % Delete these
%\makecopyright                                          % if no copyright
  %=======================================Supervisors page ===============================
\newpage    
\thispagestyle{empty}               % Don't do headers or footers.                                                  
 \begin{center}     
 SKETCH RECOGNITION AND UNDERSTANDING\\
\normalsize by      \\ 
  Maha Mohamed Nabeel El Meseery Moustafa El Meseery\\
\vspace*{0.4in}        
\normalsize
A Thesis Submitted To the\\
Faculty of Engineering, Cairo University\\
in Partial Fulfillment of the\\
Requirements for the Degree of\\
MASTER OF SCIENCE
in\\
COMPUTER ENGINEERING\\
\vspace*{0.4in} 
Under the Supervision of 
\end{center}
  \vspace*{0.4in} 
\begin{center}
 		\begin{tabular}{ccc}
		Dr. Nevin Darwish  & Dr. Samia Mashali & Dr. Magda Fayek \\
		 Professor   & Professor & Associate Professor  \\
		 Faculty of Engineering& Electronic Research Institute & 		 Faculty of Engineering \\
		  Cairo University && Cairo University\\
		\end{tabular}
\end{center}
  \vspace*{0.4in}       
  \vfill
\begin{center}
   Faculty of Engineering, Cairo University \\ Giza, Egypt \\ 2009
\end{center}

@@

%\begin{spacing}{2}
% \makebox[5in]{\hrulefill}\\ 
%Professor Nevin Darwish, Thesis Main Advisor\\
% \makebox[5in]{\hrulefill}\\ 
%Professor Samia Mashali,Thesis Advisor \\
% \makebox[6in]{\hrulefill}\\  
%Assoc. Professor Magda Fayek,Thesis Advisor\\ 
% \makebox[5in]{\hrulefill}\\ 
%Professor  Ashraf Abd El Wahab, Member\\
% \makebox[6in]{\hrulefill}\\ 
%Professor Mohamed Zaki Abd ElMegeed, Member\\
% \makebox[6in]{\hrulefill}\\ 
 %\end{spacing}
 \begin{center}
   Faculty of Engineering, Cairo University \\ Giza, Egypt \\  2009
\end{center}
  % \\   you need...\\
%\makeapproval                                           %

@@

 I thank my family and friends for their moral and support. I specifically thank, Dina Said, Noha Mansour and Marwah Shafee. Thanks, for being always there when I needed you the most. I hope to express my gratitude to all of you for supporting me and praying for me through all these years.
 %Finally, I am very grateful to my dear parents, my family, and my friends whom I consider
%as my sisters. I would like to thank particularly Radwa Aboudina, Fatma Nada, Maha
%Nabil, Haidi Badr, and Marwa Kamal. Thank you all for being always there when I needed
%you most. Thank you for believing in me and supporting me through all these years. I think
%without your support and your prayers, none of this work would be accomplished.
%ii
 \end{acknowledgments}                                   %
